Run-Time Monitoring with Adjustable Overheads \\Using Dataflow-Guided Filtering

### 2015-01-03 conclusion.tex
Updated data.

Parallel run-time monitoring techniques are attractive solutions for improving
the reliability, security, and debugging capabilities of systems. In this
paper, we have presented an architecture that enables adjustable overheads through partial monitoring. 
The architecture uses a dataflow tracking engine to prevent false positives
through tracking invalidation information. In addition, we show how the
architecture can be extended to enable null metadata filtering.
Given this architecture, we explore the design choices related to the dropping policy.
With partial monitoring, we see that with a 1.5x overhead target, BC can still
achieve 82\% average coverage and UMC and LS can still achieve 43\%  and 94\%
average coverage respectively.
At this overhead target, IMP shows less than 3\% error on average.

>>>>

Parallel run-time monitoring techniques are attractive solutions for improving
the reliability, security, and debugging capabilities of systems. In this
paper, we have presented an architecture that enables adjustable overheads through partial monitoring. 
The architecture uses a dataflow tracking engine to prevent false positives
through tracking invalidation information. In addition, we show how the
architecture can be extended to enable null metadata filtering.
Given this architecture, we explore the design choices related to the dropping policy.
With partial monitoring, we see that with a 1.5x overhead target, BC can still
achieve 85\% average coverage and UMC can still achieve 14\% 
average coverage.
At this overhead target, IMP shows less than 2\% error on average.
LS can be pushed down to 1.1x overhead and still achieve 61\% average coverage.

### 2015-01-03 evaluation.tex
Updated data.

We tested our system using benchmarks from SPECint
CPU2006 \cite{spec2006}. Since our implementation of BC depends on the
modification of {\tt malloc} to set array bounds information, we focus on the C
SPECint benchmarks. Although we do not
show results for the C++ benchmarks, we note that the results for UMC, DIFT, and IMP
for these benchmarks are similar to the other results shown.
We simulated each benchmark for 2 billion instructions. 
% An initial slack of 2
% million cycles, which is less than 1\% of
% the total execution time, is given for a 1.1x target overhead. This initial
% slack is scaled proportionally for other overhead targets.

Since LockSet race detection requires multi-threaded programs, we tested it using
the applications from the SPLASH-2 benchmark set \cite{splash-isca95}. We ran these benchmarks for
200 million instructions each using 2 main cores to run the benchmark application.
Each main core was connected to a dataflow engine and a monitoring core.

@@

Figure~\ref{fig:evaluation.filtering} shows the
execution times of performing monitoring with null filtering enabled normalized
to the execution time of the benchmarks without monitoring. UMC sees normalized
execution times of 1.7-7x with an average of 4x.
For BC, normalized execution
are 3x on average and range from 1.1x to 8.3x.
% This is not surprising since in the baseline
% implementation all loads and stores needed to be monitored. However, with
% filtering, only loads and stores corresponding to arrays need to be forwarded.
DIFT sees an average of 1.1x slowdown with a maximum slowdown of 1.3x with null
metadata filtering. This low overhead is due to the fact
that for our implementation of DIFT on SPEC
benchmarks, we only mark data read from files as tainted. Instead, if we
targeted network or streaming applications, which have larger amounts of
untrusted input data, we would observe higher overheads. IMP shows normalized
execution times of 2-6x with an average of 4x. Overheads for LS (not pictured)
applied to the SPLASH-2 benchmarks are
1.03-1.72x after null metadata filtering and the average
overhead observed is 1.33x.
Our baseline system and overheads are similar to previous multi-core
monitoring systems such as LBA-accelerated \cite{lba-isca08} and FADE
\cite{fade-hpca14} (see
Table~\ref{tab:monitoring.previous_overheads}). In
Section~\ref{sec:evaluation.fpga}, we also evaluate a higher performance, FPGA-based
monitor that shows low tens of percent of overhead.

@@

In this section, we evaluate the effectiveness of
using partial monitoring to trade-off coverage for reduced overheads.
For these results, we use a slack-based, unrestricted dropping policy.
Figure~\ref{fig:evaluation.bc_sweep} shows the monitoring coverage achieved by
array bounds check as we vary the overhead budget. 
We define \emph{monitoring coverage} as the 
percentage of dynamic checks that are performed 
(indirect jumps in DIFT, loads in UMC, and memory accesses in BC and LS). 
The metric is chosen to understand
how likely an error/attack instance is to be detected on an individual system, 
assuming that errors/attacks are uniformly distributed across checks. While
this is not necessarily true for actual errors/attacks, we believe this metric
provides a good initial estimate of the detection capabilities of the system.
%While we could not evaluate real errors/attacks due to difficulty in setting up
%a large number of bugs and exploits, we believe that the percentage of checks
%provides a good estimate of detection probability when errors/attacks are 
%uniformly distributed across checks.
Note that this metric is different from the
percentage of monitoring events that are not dropped, which includes
non-check instructions.
In the figure, the bottom portion of each
bar shows the coverage for a 1.1x overhead target and the additional
coverage for increased overhead targets are stacked above this.

We see that by varying the overhead budget, the coverage achieved also varies.
With only a 1.1x overhead target (10\% slowdown), array bounds check still
achieves 84\% monitoring coverage on average. The high coverage
achieved with such low overheads is due to two main effects.  The first is that
monitoring can be done in parallel, providing a certain level of monitoring coverage without
introducing overheads. The second effect is that there may still exist a large number of
monitoring events that do not lead to security or reliability checks. As a
result, dropping these events can reduce overheads without a large impact on
monitoring coverage.

Figure~\ref{fig:evaluation.umc_sweep} shows the analogous graph for UMC. Again
we see that varying overhead budgets enables partial monitoring. We see that
with a 1.1x overhead target, UMC achieves 25\% monitoring coverage on average.
By increasing this overhead budget to 1.5x, UMC achieves 43\% coverage on
average. Even higher coverage can be achieved by allowing higher overheads.
Similarly, Figure~\ref{fig:evaluation.ls_sweep} shows the coverage achieved by LS.
With a 1.1x overhead, LS achieves 53\% coverage on average. This increases to
71\% coverage with a 1.2x overhead. 
For DIFT (not pictured), an overhead target of 1.1x is enough for
all benchmarks tested to reach 100\% coverage.
%Since the overheads of DIFT are low to begin with, setting an overhead target
%1.1x is enough for all benchmarks tested to reach 100\% coverage.

The instruction-mix profiling monitor does not perform check operations. Thus,
the concept of coverage is not applicable here. Instead, for each instruction
type profiled, we calculate its count as a percentage of the total instructions
monitored. We take the difference of these percentages compared to the case
when full monitoring
is performed to calculate the error. Figure~\ref{fig:evaluation.imp_sweep}
shows the min, max, and average error across
instruction types for each benchmark and for varying overheads. We see that
with a 1.1x overhead, a max error of 9\% is observed across the benchmarks and the
average error across instruction types and benchmarks is less than 2\%.

@@

In addition to evaluating our system for a core-based monitor, we also
evaluated partial monitoring on a higher performance FPGA-based monitor. This
setup is based on the FlexCore \cite{flexcore-micro10} setup and uses a
fully-pipelined monitor running on an FPGA fabric at half the frequency of the
main core. We only show results for UMC due to space constraints though other
monitors show similar trends. In this case, the full overheads of
monitoring range from 1.1-1.7x. Figure~\ref{fig:evaluation.fpga_umc_sweep} shows
the coverage achieved as we sweep the overhead target from 1.01-1.7x. We see that partial
monitoring can allow the overheads of such a system to be pushed below 10\%
while still providing over 50\% coverage.

@@

% % UMC exec time
% \begin{figure}
%   \begin{center}
%     \includegraphics[width=\columnwidth]{figs/data_umc_exec_time.pdf}
%     \vspace{-0.2in}
%     \caption{Error in meeting overhead budget for uninitialized memory check for different dropping policies.}
%     \label{fig:evaluation.umc_exec_time}
%     \vspace{-0.2in}
%   \end{center}
% \end{figure}
% 
% % UMC coverage across policies
% \begin{figure}
%   \begin{center}
%     \includegraphics[width=\columnwidth]{figs/data_umc_coverage.pdf}
%     \vspace{-0.2in}
%     \caption{Coverage for uninitialized memory check for different dropping policies.}
%     \label{fig:evaluation.umc_coverage}
%     \vspace{-0.1in}
%   \end{center}
% \end{figure}

@@

In this section we evaluate the trade-offs between unrestricted dropping and source-only dropping.
The results are shown for an overhead target of 1.5x.
Figure~\ref{fig:evaluation.umc_exec_time} shows the difference between the
overhead budget and the run-time monitoring overheads for UMC. A positive value
means that the overhead target was overshot while a negative value indicates
that the overhead budget was met. We see similar results for unrestricted
dropping and source-only dropping due to the fact that UMC consists of a large
number of short, independent monitoring dependence chains.
Figure~\ref{fig:evaluation.umc_coverage} shows the coverage of UMC for
unrestricted dropping and source-only dropping. We see that, in several cases, source-only dropping
achieves higher coverage than unrestricted dropping. On average, unrestricted
dropping achieves 46\% coverage while source-only dropping achieves 49\%
coverage. This is due
to the fact that some of the overheads of monitoring for unrestricted dropping
are being spent on wasted work as discussed in Section~\ref{sec:policies.which}.

% % BC exec time
% \begin{figure}
%   \begin{center}
%     \includegraphics[width=\columnwidth]{figs/data_bc_exec_time.pdf}
%     \vspace{-0.2in}
%     \caption{Error in meeting overhead budget for array bounds check for different dropping policies.}
%     \label{fig:evaluation.bc_exec_time}
%     \vspace{-0.2in}
%   \end{center}
% \end{figure}
% 
% % BC coverage across policies
% \begin{figure}
%   \begin{center}
%     \includegraphics[width=\columnwidth]{figs/data_bc_coverage.pdf}
%     \vspace{-0.2in}
%     \caption{Coverage for array bounds check for different dropping policies.}
%     \label{fig:evaluation.bc_coverage}
%     \vspace{-0.2in}
%   \end{center}
% \end{figure}

@@

Next, we evaluate these trade-offs between source-only dropping and unrestricted dropping for BC.
Figure~\ref{fig:evaluation.bc_exec_time} shows the overhead differences for BC
and Figure~\ref{fig:evaluation.bc_coverage} shows the coverage for BC.
From Figure~\ref{fig:evaluation.bc_exec_time}, we see that for several
benchmarks, source-only dropping fails to meet the specified overhead target.
The overshoot of the overhead target is quite high with overhead differences
of 420\% for {\tt bzip2}, 120\% for {\tt gcc}, and 1500\% for {\tt hmmer}.
Since only infrequently occurring array allocations are considered as source events for BC, it can be 
difficult for source-only dropping to match overhead targets. Although
Figure~\ref{fig:evaluation.bc_coverage} shows higher coverage for
source-only dropping, this is largely due to the fact that is running with
higher overheads.

From these results, we see that for monitors with many short, independent
chains, such as UMC, source-only dropping can provide better coverage than
unrestricted dropping with the same overhead. For other monitors, such as BC,
source-only dropping is prone to overshoot the overhead target.
Thus, for applications where staying within an overhead target is especially
important, such as soft real-time systems, a slack-based, unrestricted dropping
policy is more appropriate. On the other hand, if maximum coverage is desired
and occasional slowdowns are acceptable, then source-only dropping can provide
better coverage on average.

@@

% Multi-run coverage with unrestricted dropping
\begin{figure}
  \begin{center}
    \includegraphics[width=\columnwidth, clip=true, trim=0 0.3in 0 0.1in]{figs/data_multirun_coverage.pdf}
    \vspace{-0.1in}
    \caption{Coverage over multiple runs for BC with a 10\% probability to not drop events.}
    \label{fig:evaluation.multirun}
    \vspace{-0.1in}
  \end{center}
\end{figure}

One application of partial monitoring with low overheads is to enable
cooperative debugging. 
The idea with cooperative debugging is to use partial
monitoring with very low overheads across a large number of users or runs. By
varying the pattern of partial monitoring done on each run, the goal is to
achieve high coverage across multiple runs. Varying the monitoring that is
done for different runs can be achieved by using a probabilistic dropping policy.
Figure~\ref{fig:evaluation.multirun} shows the total
coverage achieved over multiple runs for array bounds check using
unrestricted and source-only dropping policies with probabilistic dropping.
These numbers are averaged across all benchmarks. Here, we use a 10\%
probability
that events are not dropped. Since the goal is code coverage, coverage here is
measured as the percentage of static instructions which are monitored in at
least one of the runs. Each run
was simulated for 200 million instructions. 
We see that for the unrestricted dropping policy there is almost no increase in
coverage.  This is due to the fact that it is likely that at least one
monitoring event in a metadata dependence chain will be dropped with the unrestricted dropping
policy. 
Instead, source-only
dropping is much better suited for achieving high coverage over multiple runs.
Source-only dropping shows a 5\% increase in coverage with only seven runs.
Over many runs, source-only dropping should be able to
reach 100\% code coverage.

>>>>

We tested our system using benchmarks from SPECint
CPU2006 \cite{spec2006}. Since our implementation of BC depends on the
modification of {\tt malloc} to set array bounds information, we focus on the C
SPECint benchmarks. Although we do not
show results for the C++ benchmarks, we note that the results for UMC, DIFT, and IMP
for these benchmarks are similar to the other results shown.
We fast-forwarded each benchmark for 1 billion instructions and then simulated for 2 billion instructions. 
% An initial slack of 2
% million cycles, which is less than 1\% of
% the total execution time, is given for a 1.1x target overhead. This initial
% slack is scaled proportionally for other overhead targets.

Since LockSet race detection requires multi-threaded programs, we tested it using
the applications from the SPLASH-2 benchmark set \cite{splash-isca95}. 
Each benchmark was run using 2 main cores to run the benchmark application.
{\tt fmm} and {\tt raytrace} were run without fast-forwarding because they ran to completion in under 2 billion instructions.
Each main core was connected to a dataflow engine and a monitoring core.

@@

Figure~\ref{fig:evaluation.filtering} shows the
execution times of performing monitoring with null filtering enabled normalized
to the execution time of the benchmarks without monitoring. UMC sees normalized
execution times of 2.6-9.8x with an average of 5.7x.
For BC, normalized execution
are 2.7x on average and range from 1.02x to 13.6x.
% This is not surprising since in the baseline
% implementation all loads and stores needed to be monitored. However, with
% filtering, only loads and stores corresponding to arrays need to be forwarded.
DIFT sees an average of 1.1x slowdown with a maximum slowdown of 1.3x with null
metadata filtering. This low overhead is due to the fact
that for our implementation of DIFT on SPEC
benchmarks, we only mark data read from files as tainted. Instead, if we
targeted network or streaming applications, which have larger amounts of
untrusted input data, we would observe higher overheads. IMP shows normalized
execution times of 1.6-9.5x with an average of 5.8x. Overheads for LS (not pictured)
applied to the SPLASH-2 benchmarks are
1.03-1.72x after null metadata filtering and the average
overhead observed is 1.33x.
Our baseline system and overheads are similar to previous multi-core
monitoring systems such as LBA-accelerated \cite{lba-isca08} and FADE
\cite{fade-hpca14} (see
Table~\ref{tab:monitoring.previous_overheads}). In
Section~\ref{sec:evaluation.fpga}, we also evaluate a higher performance, FPGA-based
monitor that shows low tens of percent of overhead.

@@

In this section, we evaluate the effectiveness of
using partial monitoring to trade-off coverage for reduced overheads.
For these results, we use a slack-based, unrestricted dropping policy.
Figure~\ref{fig:evaluation.bc_sweep} shows the monitoring coverage achieved by
array bounds check as we vary the overhead budget. 
We define \emph{monitoring coverage} as the 
percentage of dynamic checks that are performed 
(indirect jumps in DIFT, loads in UMC, and memory accesses in BC and LS). 
The metric is chosen to understand
how likely an error/attack instance is to be detected on an individual system, 
assuming that errors/attacks are uniformly distributed across checks. This may
not necessarily be true for actual errors/attacks and so the reported coverage
may not be the same as the probability of detecting actual errors/attacks.
However, we believe this metric
provides a good initial estimate of the detection capabilities of the system.
%While we could not evaluate real errors/attacks due to difficulty in setting up
%a large number of bugs and exploits, we believe that the percentage of checks
%provides a good estimate of detection probability when errors/attacks are 
%uniformly distributed across checks.
Note that this metric is different from the
percentage of monitoring events that are not dropped, which includes
non-check instructions.
In the figure, the bottom portion of each
bar shows the coverage for a 1.1x overhead target and the additional
coverage for increased overhead targets are stacked above this.

We see that by varying the overhead budget, the coverage achieved also varies.
With only a 1.1x overhead target (10\% slowdown), array bounds check still
achieves over 80\% monitoring coverage on average. The high coverage
achieved with such low overheads is due to two main effects.  The first is that
monitoring can be done in parallel, providing a certain level of monitoring coverage without
introducing overheads. The second effect is that there may still exist a large number of
monitoring events that do not lead to security or reliability checks. As a
result, dropping these events can reduce overheads without a large impact on
monitoring coverage.

Figure~\ref{fig:evaluation.umc_sweep} shows the analogous graph for UMC. Again
we see that varying overhead budgets enables partial monitoring.
With a 2x overhead target, UMC achieves 22\% monitoring coverage on average and with a 4x overhead target, this increases to 49\%.
%We see that
%with a 1.1x overhead target, UMC achieves 25\% monitoring coverage on average.
%By increasing this overhead budget to 1.5x, UMC achieves 43\% coverage on
%average. 
Even higher coverage can be achieved by allowing higher overheads.
Similarly, Figure~\ref{fig:evaluation.ls_sweep} shows the coverage achieved by LS.
With only a 1.01x overhead, LS achieves 30\% coverage on average. This increases to
71\% coverage with a 1.1x overhead. 
For DIFT (not pictured), an overhead target of 1.1x is enough for
all benchmarks tested to reach 100\% coverage.
%Since the overheads of DIFT are low to begin with, setting an overhead target
%1.1x is enough for all benchmarks tested to reach 100\% coverage.

The instruction-mix profiling monitor does not perform check operations. Thus,
the concept of coverage is not applicable here. Instead, for each instruction
type profiled, we calculate its count as a percentage of the total instructions
monitored. We take the difference of these percentages compared to the case
when full monitoring
is performed to calculate the error. Figure~\ref{fig:evaluation.imp_sweep}
shows the min, max, and average error across
instruction types for each benchmark and for varying overheads. We see that
with a 1.1x overhead, a max error of 9\% is observed across the benchmarks and the
average error across instruction types and benchmarks is 3\%.

@@

In addition to evaluating our system for a core-based monitor, we also
evaluated partial monitoring on a higher performance FPGA-based monitor. This
setup is based on the FlexCore \cite{flexcore-micro10} setup and uses a
fully-pipelined monitor running on an FPGA fabric at half the frequency of the
main core. We only show results for UMC due to space constraints though other
monitors show similar trends. In this case, the full overheads of
monitoring range from 1.1-1.7x. Figure~\ref{fig:evaluation.fpga_umc_sweep} shows
the coverage achieved as we sweep the overhead target from 1.01-2.0x. We see that partial
monitoring can allow the overheads of such a system to be pushed below 10\%
while still providing 45\% coverage.

@@

@@

In this section we evaluate the trade-offs between unrestricted dropping and source-only dropping.
The results are shown for an overhead target of 2.0x for UMC and 1.5x for BC.
Figure~\ref{fig:evaluation.umc_exec_time} shows the difference between the
overhead budget and the run-time monitoring overheads for UMC. A positive value
means that the overhead target was overshot while a negative value indicates
that the overhead budget was met. For most benchmarks, we see similar results for unrestricted
dropping and source-only dropping due to the fact that UMC consists of a large
number of short, independent monitoring dependence chains. Source-only dropping
causes overshoot of the overhead target for {\tt hmmer} and {\tt h264ref}.
Figure~\ref{fig:evaluation.umc_coverage} shows the coverage of UMC for
unrestricted dropping and source-only dropping. We see that, in several cases, source-only dropping
achieves higher coverage than unrestricted dropping while still closely matching the overhead target. For example, {\tt perlbench} shows a 10\% increase in coverage and {\tt libquantum} shows an 18\% increase in coverage by using source-only dropping. This is due
to the fact that some of the overheads of monitoring for unrestricted dropping
are being spent on wasted work as discussed in Section~\ref{sec:policies.which}.

@@

Next, we evaluate these trade-offs between source-only dropping and unrestricted dropping for BC.
Figure~\ref{fig:evaluation.bc_exec_time} shows the overhead differences for BC
and Figure~\ref{fig:evaluation.bc_coverage} shows the coverage for BC.
From Figure~\ref{fig:evaluation.bc_exec_time}, we see that for several
benchmarks, source-only dropping fails to meet the specified overhead target.
The overshoot of the overhead target is quite high with overhead differences over 100\% for {\tt bzip2}, {\tt hmmer}, and {\tt h264ref}.
Since only infrequently occurring array allocations are considered as source events for BC, it can be 
difficult for source-only dropping to match overhead targets. Although
Figure~\ref{fig:evaluation.bc_coverage} shows higher coverage for
source-only dropping, this is largely due to the fact that is running with
higher overheads.

From these results, we see that depending on the monitor and the program
behavior, source-only dropping can provide better coverage than unrestricted
dropping with the same overhead. Overall, unrestricted dropping is better at
meeting an overhead target.
Thus, for applications where staying within an overhead target is especially
important, such as soft real-time systems, a slack-based, unrestricted dropping
policy is more appropriate. On the other hand, if maximum coverage is desired
and occasional slowdowns are acceptable, then source-only dropping can provide
better coverage on average.

@@

% Multi-run coverage with unrestricted dropping
\begin{figure}
  \begin{center}
    \includegraphics[width=\columnwidth]{figs/data_multirun_coverage.pdf}
    \vspace{-0.3in}
    \caption{Coverage over multiple runs for BC with a 10\% probability to not drop events.}
    \label{fig:evaluation.multirun}
    \vspace{-0.3in}
  \end{center}
\end{figure}

One application of partial monitoring with low overheads is to enable
cooperative debugging. 
The idea with cooperative debugging is to use partial
monitoring with very low overheads across a large number of users or runs. By
varying the pattern of partial monitoring done on each run, the goal is to
achieve high coverage across multiple runs. Varying the monitoring that is
done for different runs can be achieved by using a probabilistic dropping policy.
Figure~\ref{fig:evaluation.multirun} shows the total
coverage achieved over multiple runs for array bounds check using
unrestricted and source-only dropping policies with probabilistic dropping.
These numbers are averaged across all benchmarks. Here, we use a 10\%
probability
that events are not dropped. Since the goal is code coverage, coverage here is
measured as the percentage of static instructions which are monitored in at
least one of the runs. Each run
was simulated for 500 million instructions. 
We see that for the unrestricted dropping policy there is almost no increase in
coverage.  This is due to the fact that it is likely that at least one
monitoring event in a metadata dependence chain will be dropped with the unrestricted dropping
policy. 
Instead, source-only
dropping is much better suited for achieving high coverage over multiple runs.
Source-only dropping shows a 6\% increase in coverage with only eight runs.
With more runs, source-only dropping should be able to
reach 100\% code coverage.

### 2015-01-03 introduction.tex
Various edits throughout paper.
Updated data.

% Adjustable overhead
Partial monitoring with adjustable overheads is achieved by dynamically
dropping monitoring operations when overheads exceed a specified overhead
budget. Although this results in reduced monitoring coverage (i.e., false
negatives), false positives can also occur due to out-of-date metadata information.
In order to prevent these
false positive, we need to track the dropped metadata flows.  We present a
hardware-based dataflow tracking engine that keeps track of these dropped
flows. With this architecture, we investigate different policies for deciding
which events to drop for partial monitoring. These different policies show a
trade-off between closely matching the overhead budget and the monitoring
coverage achieved.
In addition to enabling partial monitoring, we show how a simple
extension to our dataflow engine enables this null metadata filtering.
For example, for an array bounds check, checking non-pointer accesses is
unnecessary and can be filtered out using the dataflow engine.

@@

% Evaluation
In order to evaluate our approach, we applied it to five different monitoring
techniques. These monitoring techniques vary in what events they monitor, the
size and semantics of their metadata, and the operations performed on metadata.
% Our experiments show that filtering reduces the average overhead of these
% monitors from 7-18x down to 13-300\%.
% In addition, with partial monitoring, for the monitoring schemes which still
% see average overheads of 300\%, we show that with just 10\% overheads, we can still
% provide 32-82\% of coverage on average. By increasing the
% overhead budget, this coverage rate can be increased. 
These monitors show slowdowns of 1.1-4.3x with the null metadata filtering when
implemented on a multi-core platform.
Our results show that the partial monitoring can still achieve significant
coverage with reduced overheads. For example, for monitors which showed 3-4x
average overheads, slowdown could be reduced to 1.5x while still achieving a
coverage of 43-82\% on average.

>>>>

% Adjustable overhead
Partial monitoring with adjustable overheads is achieved by dynamically
dropping monitoring operations when overheads exceed a specified overhead
budget. Although this results in reduced monitoring coverage (i.e., false
negatives), false positives can also occur due to out-of-date metadata information.
In order to prevent these
false positive, we need to track the dropped metadata flows.  We present a
hardware-based dataflow tracking engine that keeps track of these dropped
flows. With this architecture, we investigate different policies for deciding
which events to drop for partial monitoring. These different policies show a
trade-off between closely matching the overhead budget and the monitoring
coverage achieved.
In addition to enabling partial monitoring, we show how a simple
extension to our dataflow engine can enable null metadata filtering.
For example, for an array bounds check, checking non-pointer accesses is
unnecessary and can be filtered out using the dataflow engine.

@@

% Evaluation
In order to evaluate our approach, we applied it to five different monitoring
techniques. These monitoring techniques vary in what events they monitor, the
size and semantics of their metadata, and the operations performed on metadata.
% Our experiments show that filtering reduces the average overhead of these
% monitors from 7-18x down to 13-300\%.
% In addition, with partial monitoring, for the monitoring schemes which still
% see average overheads of 300\%, we show that with just 10\% overheads, we can still
% provide 32-82\% of coverage on average. By increasing the
% overhead budget, this coverage rate can be increased. 
These monitors show average slowdowns of 1.1-5.8x with the null metadata filtering when
implemented on a multi-core platform.
Our results show that the partial monitoring can still achieve significant
coverage with reduced overheads. For example, for the monitors which showed over 2x
average overheads, slowdown could be cut to 1.5x while still achieving a
coverage of 14-85\% on average.

### 2015-01-03 title.tex
Update to camera-ready formatting.
Updated data.

\ifanonymized{\author{Anonymized}}
{\author{Daniel Lo, Tao Chen, Mohamed Ismail, and G. Edward Suh}}

\date{}
\maketitle

@@

Recent studies have proposed various parallel run-time monitoring techniques to
improve the reliability, security, and debugging capabilities of computer
systems. However, these run-time monitors can introduce large performance and energy
overheads, especially for flexible systems that support a range of monitors.
%Traditionally, these overheads have been an
%all-or-nothing cost; monitoring cannot be used if the overheads are considered
%too large.  
In this paper, we introduce a hardware dataflow tracking engine that enables
adjustable overheads through partial monitoring. This allows a trade-off to be
made between monitoring coverage and overhead. This dataflow engine
can also be extended to filter out monitoring operations associated with null
metadata in order to reduce overheads.
% In this paper, we introduce a hardware dataflow tracking engine that can be
% used to filter out unnecessary monitoring and enable adjustable partial monitoring.
% The dataflow engine can identify events with null metadata so that they can
% be filtered out. To further reduce the overhead of monitoring, we propose
% to enable a trade-off between monitoring coverage and overhead by dropping certain
% monitoring operations. For this partial monitoring, the dataflow engine is used
% to track dropped monitoring flows so that false positives can be avoided.
Given this architecture, we investigate how the dropping decisions should be
made for partial monitoring and show that there exist interesting policy
decisions depending on the target application of partial monitoring.
Our experimental results show that overheads can be reduced significantly 
by trading off coverage. For example, with average overheads of 3-4x for full
monitoring range, the proposed architecture can still
achieve 43-82\% coverage when the slowdown is reduced to 1.5x.

>>>>

\ifanonymized{\author{Anonymized}}
{\author{\IEEEauthorblockN{Daniel Lo, Tao Chen, Mohamed Ismail, and G. Edward Suh}
\IEEEauthorblockA{Cornell University\\
Ithaca, NY 14850, USA\\
\{dl575, tc466, mii5, gs272\}@cornell.edu}}
}

\maketitle

@@

Recent studies have proposed various parallel run-time monitoring techniques to
improve the reliability, security, and debugging capabilities of computer
systems. However, these run-time monitors can introduce large performance and energy
overheads, especially for flexible systems that support a range of monitors.
%Traditionally, these overheads have been an
%all-or-nothing cost; monitoring cannot be used if the overheads are considered
%too large.  
In this paper, we introduce a hardware dataflow tracking engine that enables
adjustable overheads through partial monitoring. This allows a trade-off to be
made between monitoring coverage and overhead. This dataflow engine
can also be extended to filter out monitoring operations associated with null
metadata in order to reduce overheads.
% In this paper, we introduce a hardware dataflow tracking engine that can be
% used to filter out unnecessary monitoring and enable adjustable partial monitoring.
% The dataflow engine can identify events with null metadata so that they can
% be filtered out. To further reduce the overhead of monitoring, we propose
% to enable a trade-off between monitoring coverage and overhead by dropping certain
% monitoring operations. For this partial monitoring, the dataflow engine is used
% to track dropped monitoring flows so that false positives can be avoided.
Given this architecture, we investigate how the dropping decisions should be
made for partial monitoring and show that there exist interesting policy
decisions depending on the target application of partial monitoring.
Our experimental results show that overheads can be reduced significantly 
by trading off coverage. For example, for monitoring techniques with average
overheads of 2-6x, the proposed architecture is able to reduce slowdowns to
1.5x while still achieving 14-85\% average coverage.
